% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{Liam O'Connor-Davis}
% \address used twice to have two lines of address

 
\begin{resume}
 
\section{SUMMARY}
I'm a computer scientist specialising in programming languages and type systems. My main interest is in dependent type theories and their use in software verification and mathematics. I have significant experience in functional programming, particularly in Haskell. I also enjoy programming in languages such as Scala and ML. I have skills in traditional formal verification and theorem proving, including work on the formally verified seL4 kernel. I also have some skill at concurrent and distributed programmming, and I'm aware of various approaches to concurrency abstraction (e.g process algebra) and concurrent data structures. I am able to structure proofs of properties on concurrent programs using standard methods. I have significant interest in mathematics, particularly proof theory, the foundations of mathematics, algebraic topology, category theory, and abstract algebra.

In the past I have developed a great deal of experience in web development, including experience at Google in the development of a new product (Google Wave). I follow closely development of new standards for the Web.

I have a moderate understanding of conversational Japanese and can read and write at a rudimentary level, and beginning study of Vietnamese.

\section{SPECIALTIES} Functional Programming; Formal Verification; Type Theory; Logic; Logic Programming; Programming Languages; Compilers; Web Development; Theorem Proving; Process Algebra; Concurrency.

\section{COMPUTING SKILLS} {\sl Programming Languages:} Haskell, Agda, Coq, Rust, Swift,
         Isabelle, Standard ML, Scheme, C, OCaml, C++, 
         Java, Scala, Clojure, Ruby, Python, 
         Erlang, Mercury. \\
         {\sl Operating Systems:} Mac OS X, Linux, BSD

\section{EDUCATION} 
                {\sl PhD (currently studying)} Computer Science\\
                University of New South Wales. In 2014 I was also affiliated
                with NICTA.
                \\ 
                \emph{Thesis topic:} ``Language-aided Systems Verification'' \\
                Focusing on the use of linear types and other PL research to
                make verifying low-level software systems for functional
                correctness cheaper and easier.
                \\
                \begin{itemize} \itemsep -2pt % reduce space between items
                    \item NICTA Impact Award Recipient, for high-impact trustworthy systems research.
                \end{itemize}

                {\sl Bachelor of Science (Hons. 1st Cl.),} Computer Science\\
                University of New South Wales. Completed several courses with high distinction
                and earned four awards:
                \begin{itemize} \itemsep -2pt % reduce space between items
                    \item Macquarie Undergraduate Performance Award (1st Year)
                    \item CSE Undergraduate Performance Award (1st Year), 3rd Place
                    \item CSE Undergraduate Performance Award (3st Year), 3rd Place
                    \item CSE Undergraduate Performance Award (4th Year), 3rd Place
                \end{itemize}
                I had an honours thesis result that was second among all graduands, at 93.4.
                \\
                \\ 
                \emph{Honours thesis:} ``Formalising GHC's Type System'', a dependently typed formalisation
                of the type system of a Haskell compiler.\\
                \emph{Special Project:} ``PhracJS - A Lazy, Purely Functional Language for Browsers'', an investigation into the suitability of purely functional programming for the web browser via compilation to JavaScript.
Involved the implementation of a small compiler.          \\
                \emph{Special Project:} ``Gentzen - A Beginner's Theorem Prover'', a carefully designed theorem prover intended to aid in the teaching of introductory courses for formal semantics of programming languages.
 
\section{EXPERIENCE} {\sl Research Engineer} \hfill January 2013 - January 2014 \\
                 Software Systems Research Group, NICTA
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                \item  Working on Haskell DSLs for file system specification
                       for the Bilby verified file systems project.
                \item \emph{Publication:} ``File Systems Deserve Verification Too!'' \\
                        \small
                          Gabriele Keller, Toby Murray, Sidney Amani, Liam O'Connor \\
                          Zilin Chen, Leonid Ryzhyk, Gerwin Klein, Gernot Heiser \\
                          Workshop on Programming Languages and Operating Systems \\
                          November 2013
                          \normalsize

                \end{itemize}
 
                {\sl Research Assistant} \hfill March 2011 - December 2012 \\
                 Software Systems Research Group, NICTA
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Contributions to the l4.verified operating system verification project.
                 \end{itemize} 
                {\sl Casual Teaching Academic} \hfill January 2009 - Present \\
                 School of Computer Science and Engineering, UNSW
                  \begin{itemize}
                    \item Teaching tutorials and lectures in courses ranging from introductory C and Java programming to
                         formal semantics of programming languages, high-assurance programming,
                         concurrency and verification.
                   \end{itemize} 
 
                {\sl Software Engineer} \hfill November 2009 - February 2010\\
                 Google
                  \begin{itemize}
                       \item Internship developing features for Google Wave.
                   \end{itemize} 

                {\sl Tech Lead} \hfill January 2008 - March 2011\\
                 Mudo Media
                  \begin{itemize}
                       \item Developing a web and facebook application for travellers to share information with each other. Developed using Haskell web frameworks (Yesod) and a RESTful API.
                   \end{itemize} 
             
                {\sl Director} \hfill May 2005 - May 2010\\
                  Innove Pty. Ltd.
                  \begin{itemize}
                       \item Chief Technical Officer, Director and Manager.
                   \end{itemize} 
 

\end{resume}
\end{document}







